%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Medium Length Professional CV
% LaTeX Template
% Version 2.0 (8/5/13)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Rishi Shah 
%
% Important note:
% This template requires the resume.cls file to be in the same directory as the
% .tex file. The resume.cls file provides the resume style used for structuring the
% document.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass{resume} % Use the custom resume.cls style

\usepackage[left=0.75in,top=0.6in,right=0.75in,bottom=0.6in]{geometry} % Document margins
\usepackage{hyperref}
\usepackage{fontawesome5}
\usepackage{amsmath}
\usepackage{enumitem}

\newcommand{\tab}[1]{\hspace{.2667\textwidth}\rlap{#1}}
\newcommand{\itab}[1]{\hspace{0em}\rlap{#1}}
\name{Arnav Sood} % Your name
\address{17 Sparrow Drive, Princeton Jct., NJ 08550} % Your address
\begin{document}

\faIcon{git-square} \href{https://github.com/arnavs}{\tt arnavs} \vline \hspace{0.5 em} {\faIcon{globe}} \href{https://arnavsood.com}{\tt arnavsood.com} \vline \hspace{0.5 em} {\faIcon{envelope}} \href{mailto:arnav@arnavsood.com}{\tt arnav@arnavsood.com} \vline \hspace{0.5 em} \faIcon{phone} (+1) 609.285.7001 \vline \hspace{0.5 em} \faIcon{passport} USA 

\begin{rSection}{Employment History}
Predoctoral Researcher, {\bf University of British Columbia} \hfill {Jun. 2018 --- Jun. 2020} 
\\ Advisor: Prof. Jesse Perla \smallskip 

Lead Developer, {\bf QuantEcon} \hfill {Jan. 2019 --- Present}
\\ References: Prof. John Stachurski, Dr. Matt McKay, Dr. Chase Coleman

Student Researcher, {\bf NSF-CUNY Treespace REU} \hfill {Fall 2016}

Research Assistant, {\bf Prof. Laura Veldkamp} \hfill {May. 2016 --- Jan. 2018}
\end{rSection}

\begin{rSection}{Education}
{\bf University of British Columbia} \hfill {Jun. 2018 --- Jun. 2020} 
\\ Selected Courses (MS and BA.)  % \hfill { A/A+ Grades }

{\bf New York University} \hfill {Sep. 2014 --- May 2018} 
\\ Bachelor of Arts (Math.) % \hfill { GPA: 3.2 } 
\\ Minors in Economics, Philosophy 
\end{rSection}

\begin{rSection}{Publications}
    {\bf Exploiting Symmetry in High-Dimensional Dynamic Programming} \hfill {In-Progress} 
    \\ (with Jesse Perla, Mahdi Kahou, Jes\'{u}s Fern\'{a}ndez-Villaverde)    

    We provide a new method for solving high-dimensional dynamic programming problems, and recursive competitive equilibria with a very large (but finite) number of heterogenous agents.  The ``curse of dimensionality'' is avoided due to three complementary techniques: (1) exploiting symmetry in the approximate law of motion and the value function when designing deep learning approximations; (2) constructing a concentration of measure to calculate high-dimensional expectations using only a \textit{single} Monte-Carlo draw for all idiosyncratic shocks; and (3) sampling methods to ensure the model fits along manifolds of interest. 
\end{rSection}

\begin{rSection}{Research Assistant Publications}
    {\bf \href{https://github.com/jlperla/PerlaTonettiWaugh.jl}{Equilibrium Technology Diffusion, Trade, and Growth}}  \hfill {Jesse Perla}
    \begin{itemize}
        \item Co-wrote Julia code which solves a forward-looking differential system in steady-state, and computes transition dynamics in response to shocks.
    \end{itemize}

    {\bf \href{https://github.com/jlperla/KnowledgeDiffusionSimulations.jl}{Knowledge Diffusion Simulations}} \hfill {Jesse Perla}
    \begin{itemize}
        \item Wrote Julia code to solve ensembles of high-dimensional jump diffusion problems and track evolution of moments.
    \end{itemize}

    {\bf \href{https://github.com/jlperla/Perla1.jl}{A Model of Product Awareness and Industry Life Cycles}} \hfill {Jesse Perla}
    \begin{itemize}
        \item Provided general assistance with Julia code.
    \end{itemize}

    % https://github.com/jlperla/PerlaPfluegerSzkup.jl
    {\bf {Limited Liability as a Financial Friction}} \hfill {Jesse Perla}
    \begin{itemize}
        \item Worked on numerical solution of the equilibrium path in Julia, and getting the software ready for publication.
    \end{itemize}

    % {\bf \href{https://github.com/jlperla/KnowledgeDiffusionSimulations.jl}{VITOR HEALTH THING}} \hfill {Vitor Farinha Luz}
    % \begin{itemize}
    %     \item Wrote Julia code to solve ensembles of high-dimensional jump diffusion problems and track evolution of moments.
    % \end{itemize}

    {\bf Taking Orders and Taking Notes: \\ \href{https://www.nber.org/papers/w22461}{Dealer Information Sharing in Financial Markets}} \hfill {Laura Veldkamp}
    \begin{itemize}
        \item Calculated equilibria and bounds for various model cases.
    \end{itemize}

    {\bf \href{https://www.aeaweb.org/articles?id=10.1257/aer.20171349}{Long-Run Growth of Financial Technology}} \hfill {Laura Veldkamp}
    \begin{itemize}
        \item Calculated various limiting facts about the economy.
    \end{itemize}

    {\bf \href{http://www.restud.com/wp-content/uploads/2019/11/MS19864manuscript.pdf}{Germs, Social Networks, and Growth}} \hfill {Laura Veldkamp}
    \begin{itemize}
        \item Implemented the network's endogenous transition process in Julia, with caching of relevant state variables.
    \end{itemize}
\end{rSection}

\begin{rSection}{Software}
    {\bf \href{https://julia.quantecon.org}{QuantEcon Julia Lectures}} % \hfill {Co-Author}
    \begin{itemize}
        \item Wrote new lectures, overhauled code, deployed to cloud backends, and supervised RAs.
    \end{itemize}

    {\bf \href{https://github.com/quantecon/Expectations.jl}{QuantEcon/Expectations.jl}} % \hfill {Research Code}
    \begin{itemize}
        \item Uses Gaussian quadrature to take expectations for increased clarity, speed, and accuracy. 
    \end{itemize}

    {\bf \href{https://github.com/quantecon/InstantiateFromURL.jl}{QuantEcon/InstantiateFromURL.jl}} % \hfill {Research Code}
    \begin{itemize}
        \item Allows Julia Jupyter notebooks to run anywhere with proper package versions. Used in QuantEcon lectures.
    \end{itemize}

    {\bf \href{https://vse.syzygy.ca}{VSE Syzygy JupyterHub}} % \hfill {Co-Author}
    \begin{itemize}
        \item Worked with Dr. Ian Allison of PIMS to maintain a JupyterHub server for faculty and student use. Deployed from Docker for reproducible setup.
    \end{itemize}
\end{rSection}

\begin{rSection}{Talks and Posters}
    % https://pretalx.com/juliacon2020/talk/87JCMX/
    {\bf Dependency-Aware Jupyter Notebooks} \hfill {JuliaCon 2020}

    % https://live.juliacon.org/uploads/posters/N9CXCT.pdf
    {\bf Extending Distributions with Expectations.jl} \hfill {JuliaCon 2020}
\end{rSection}

\begin{rSection}{Teaching}
    {\bf University of British Columbia} \hfill {Jun. 2018 --- Jun. 2020}
    \\ Guest Lecturer, ECON 622 (2019) and ECON 628 (2018)
    \begin{itemize}
        \item Prepared and taught occasional lectures to PhD students on software design in Julia.
        \item Helped students with assignment difficulties.
    \end{itemize}

\end{rSection}



\end{document}
