%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Medium Length Professional CV
% LaTeX Template
% Version 2.0 (8/5/13)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Rishi Shah 
%
% Important note:
% This template requires the resume.cls file to be in the same directory as the
% .tex file. The resume.cls file provides the resume style used for structuring the
% document.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass{resume} % Use the custom resume.cls style

\usepackage[left=0.75in,top=0.6in,right=0.75in,bottom=0.6in]{geometry} % Document margins
\usepackage{hyperref}
\usepackage{fontawesome5}
\usepackage{amsmath}
\usepackage{enumitem}

\newcommand{\tab}[1]{\hspace{.2667\textwidth}\rlap{#1}}
\newcommand{\itab}[1]{\hspace{0em}\rlap{#1}}
\name{Arnav Sood} % Your name
\address{2001-1600M Beach Ave, Vancouver V6G 1Y7 Canada} % Your address
\begin{document}

\faIcon{git-square} \href{https://github.com/arnavs}{\tt arnavs} \vline \hspace{0.5 em} {\faIcon{globe}} \href{http://arnavsood.com}{\tt http://arnavsood.com} \vline \hspace{0.5 em} \faIcon{phone} (+1) 604.339.1784 \vline \hspace{0.5 em} \faIcon{passport} USA \vline \hspace{0.5 em} \faIcon{birthday-cake} 1996

\begin{rSection}{Employment History}
Predoctoral Researcher, {\bf University of British Columbia} \hfill {Jun. 2018 --- Present} 
\\ Advisor: Prof. Jesse Perla \smallskip 

Lead Developer, {\bf QuantEcon} \hfill {Jan. 2019 --- Present}
\\ References: Prof. John Stachurski, Dr. Matt McKay, Dr. Chase Coleman

Research Assistant, {\bf Prof. Laura Veldkamp} \hfill {May. 2016 --- Jan. 2018}
\end{rSection}


\begin{rSection}{Education}

{\bf University of British Columbia} \hfill {Jun. 2018 --- Present} 
\\ Selected Courses (MS and BA.)  % \hfill { A/A+ Grades }

{\bf New York University} \hfill {Sep. 2014 --- May 2018} 
\\ Bachelor of Arts (Math.) % \hfill { GPA: 3.2 } 
\\ Minors in Economics, Philosophy 
\end{rSection}

\begin{rSection}{Projects}

{\bf Expectations.jl} \hfill {{\faIcon{git-square} \href{https://github.com/QuantEcon/Expectations.jl}{\tt QuantEcon/Expectations.jl}}} \smallskip
\\ Wrap \texttt{Distributions.jl} objects in lightweight, callable expectation operators that accept functional arguments (e.g., \verb|E(x -> x^2|.) Uses specialized Gaussian quadrature rules for performance and accuracy. 

{\bf PerlaTonettiWaugh.jl} \hfill {\faIcon{git-square} \href{https://github.com/jlperla/PerlaTonettiWaugh.jl}{\tt jlperla/PerlaTonettiWaugh.jl}} \smallskip
\\ Solves a differential system in steady state; implementing the model as a Differential Algebraic Equation (DAE); and writing code to handle transition dynamics in response to shocks. Joint with Chiyoung Ahn. 

{\bf QuantEcon Julia Lectures} \hfill {\faIcon{globe} \href{https://julia.quantecon.org}{\tt julia.quantecon.org}} \smallskip
\\ Writing new lectures, updating all code to Julia 1.x, deploying cloud backends, and project management/code review. Joint work with many people.

{\bf vse.syzygy.ca} \hfill {\faIcon{git-square} \href{https://github.com/ubcecon/vse-jupyterhub}{\tt ubcecon/vse-jupyterhub}} \smallskip
\\ Work with Dr. Ian Allison of PIMS to maintain a JupyterHub server for departmental use. Deployed from Docker for a reproducible configuration. 

{\bf Germs, Social Networks, and Growth} \hfill {\faIcon{git-square} \href{https://github.com/arnavs/networks-paper}{\tt arnavs/networks-paper}} \smallskip
\\ Julia implementation of Prof. Veldkamp's paper of the same name. 
\end{rSection}

\begin{rSection}{Skills}
Julia, Docker, Open-Source Development, Economic Programming, Differential Equations
\end{rSection}

\end{document}
