% !TEX program = xelatex

%%% A template to produce a nice-looking Curriculum Vitae.
%%% Borrowed from Kieran Healy <kjhealy@gmail.com> and Simon Munzert <munzert@hertie-school.org>
%%% Most recent version is at http://kjhealy.github.com/kjh-vita

\documentclass[10pt,article,oneside]{memoir}   % based on locally stored memoir-article-styles.sty
\usepackage{org-preamble-xelatex} % based on locally stored org-preamble-xelatex.sty
\usepackage{url}
\usepackage{amssymb}
\usepackage{listings}
\usepackage{datetime}
\usepackage[top=1in, bottom=1in, left=4cm, right=3cm, heightrounded, marginparwidth=2.5cm, marginparsep=5mm]{geometry}
\newdateformat{monthyeardate}{%
  \monthname[\THEMONTH], \THEYEAR}

% ------ fonts ------%
\usepackage{textcomp}
\usepackage{fontspec}
\defaultfontfeatures{
Path = /usr/local/texlive/2021/texmf-dist/fonts/opentype/public/fontawesome5/ }
\usepackage{fontawesome5}
\usepackage{crimson}
\usepackage{enumitem}% http://ctan.org/pkg/enumitem
\setlist[itemize]{noitemsep, topsep=0in}

\definecolor{darkred}{rgb}{0.68,0.10,0.10}

\usepackage{soul}

%% Custom hanging indent for vita items
\def\mybibind{\vspace{0.1in} \noindent \hangindent=1 true cm\hangafter=1}


% penalize stuff
\clubpenalty = 10000      % Schusterjungen
\widowpenalty = 10000          % Hurenkinder
\displaywidowpenalty = 10000   % Hurenkinder

% header
\usepackage{fancyhdr}
\pagenumbering{gobble}

%%%------------------------------------------------------------------------
%%% Metadata
%%%------------------------------------------------------------------------
\def\myauthor{Arnav Sood}
\def\mytitle{Vita}
\def\mycopyright{\myauthor}
\def\mykeywords{}
\def\mybibliostyle{plain}
\def\mybibliocommand{}
\def\mysubtitle{}
\def\myemail{arnav@arnavsood.com}
\def\myweb{arnavsood.com}
\def\mygit{arnavs}
\def\myphone{(+1) 609 285 7001}
\def\myaffiliation{University of British Columbia}
% \def\myuni{B.A. Math (NYU)}
% \def\myoffice{053 Iona Building}
\date{\today}
\def\mykeywords{Arnav, Sood, Arnav Sood, Vita, CV, Resume, Economics}
% \setlength{\parskip}{1em}

\usepackage{hyphenat}
%\setlength{\emergencystretch}{10pt}
\hyphenation{Bun-des-tags-wah-len}
\hyphenation{Wahl-kreis-ebe-ne}
\hyphenation{Con-sti-tu-ents}
\hyphenation{Kan-di-da-ten-be-ur-tei-lung}
\hyphenation{Mann-heim}
\hyphenation{ge-winnt}
\hyphenation{Clau-dius}

\rhead{
  % \fontfamily{SourceSansPro-LF}\selectfont obsolete
  \flushright \small
  ~ \\
  % \myphone ~~ \faPhone \\
 {\small  \href{mailto:\myemail}{\texttt{\myemail}} ~~\faEnvelope} \\
 {\small  \href{https://\myweb}{\texttt{\myweb}} ~~\faGlobe} \\
 {\small  \href{https://github.com/\mygit}{\texttt{\mygit}} ~~\faGit} \\
 {\small  US citizen, Canada PR ~~\faPassport} \\ 
}
\lhead{ {\small  Compiled \today} \\ 
\hspace{1 em} \\ 
\hspace{1 em} \\ }
% \setlength\headheight{50pt}
\renewcommand{\headrulewidth}{0pt}

%%%------------------------------------------------------------------------
%%% Document
%%%------------------------------------------------------------------------
\begin{document}

\newcommand{\marginhead}[1]{\marginpar{{\flushleft \footnotesize\vspace{-1em} \textsf{\textcolor{darkred}{#1}}}}}
%% No bullets on labels
\renewcommand{\labelitemi}{~}


%%%------------------------------------------------------------------------
%%% Page layout
%%%------------------------------------------------------------------------

% \pagestyle{empty}
\pagestyle{fancy}

%%%------------------------------------------------------------------------
%%% Address and contact block
%%%------------------------------------------------------------------------
\hfill

%% Name
\vspace{0.4in}
\noindent{\LARGE \textbf{ARNAV SOOD}}  
\reversemarginpar

{\vskip 1em}
\bigskip

%% Overview
\marginhead{\textsf{overview}}
\setlength{\parindent}{1cm}

I am a first-year economics Ph.D. student at Carnegie Mellon University (Tepper School of Business.) My general interests are in computational macroeconomics, and especially high-dimensional models with heterogeneity in information. 

{\vskip 1em}
\bigskip

%% Employment
\marginhead{employment}
\setlength{\leftskip}{0cm}

Predoctoral Fellow, Univeristy of British Columbia, 2018--2020.
\begin{itemize}
  \setlength{\leftskip}{1cm} \item ${\color{darkred} \blacktriangleright}$ Supervised by \href{https://jesseperla.com}{Jesse Perla}. Member of \href{https://caida.ubc.ca/faculty-members-caida}{CAIDA}. 
\end{itemize} \vspace{0.1in} 

Lead Developer, QuantEcon, 2019--. 

{\vskip 1em}
\bigskip

%% Education
\setlength{\leftskip}{0cm}
\marginhead{education}

\emph{(In-Progress) Ph.D. Economics, Carnegie Mellon University}. \vspace{0.1in}

B.A. Mathematics, New York University, 2018.

{\vskip 1em}
\bigskip

\setlength{\leftskip}{0cm}
\marginhead{working papers}

\textbf{\href{https://www.nber.org/papers/w28981}{Exploiting Symmetry in High-Dimensional Dynamic Programming}}. \hfill NBER
\begin{itemize}
  \setlength{\leftskip}{1cm} \item  With Mahdi Ebrahimi Kahou, Jes\'{u}s Fern\'{a}ndez-Villaverde, Jesse Perla.
  \item \emph{Presented}: Minnesota Macro Conference (Minneapolis MN, August 2--4, 2021); VSE Econometrics Lunch (Vancouver BC, April 16, 2021); VSE Lunch Seminar (Vancouver BC, December 1, 2020)
\end{itemize} 

{\vskip 1em}
\bigskip

\setlength{\leftskip}{0cm}
\marginhead{software}

\textbf{\href{https://github.com/QuantEcon/expectations.jl}{Expectations.jl}}  
\begin{itemize}
  \setlength{\leftskip}{1cm} \item  Efficient expectation operators for univariate distributions, using Gaussian quadrature. 
  \item \emph{Presented}: \href{https://live.juliacon.org/uploads/posters/N9CXCT.pdf}{JuliaCon 2020} (Virtual, July 29--31, 2020) 
\end{itemize} \vspace{0.1in}

\textbf{\href{https://github.com/QuantEcon/InstantiateFromURL.jl}{InstantiateFromURL.jl}}  
\begin{itemize}
  \setlength{\leftskip}{1cm} \item  Allows Julia notebooks to refer to online, versioned dependency information. 
  \item \emph{Presented}: \href{https://live.juliacon.org/talk/87JCMX}{JuliaCon 2020} (Virtual, July 29--31, 2020) 
\end{itemize} 

{\vskip 1em}
\bigskip

\marginhead{other writing}
\setlength{\leftskip}{0cm}

\textbf{\href{https://notes.quantecon.org/submission/5c832d2be7b4c5000f4c8e48}{Optimal Stopping and Linear Complementarity}}. \hfill QuantEcon Notes
\begin{itemize}
  \setlength{\leftskip}{1cm} \item  With Jesse Perla. \href{https://quantecon.github.io/SimpleDifferentialOperators.jl/v0.4/generated/LCP_advanced.html}{Computational Appendix}.
\end{itemize} \vspace{0.1in}


\textbf{\href{https://dailysciencefiction.com/science-fiction/other-worlds-sf/arnav-sood/local-perturbation}{Local Perturbation}}.  \hfill Daily Science Fiction
\begin{itemize}
  \setlength{\leftskip}{1cm} \item  Applied comparative statics. 
\end{itemize} \vspace{0.1in}


\textbf{\href{https://dailysciencefiction.com/fantasy/fantasy/arnav-sood/customer-feedback-secondhand-alchemical-goods}{Customer Feedback (Secondhand Alchemical Goods)}}. \hfill Daily Science Fiction
\begin{itemize}
  \setlength{\leftskip}{1cm} \item  Discussion of various transmutation schemes.  \href{https://microverses.net/archives/250}{Microverses Review}.
\end{itemize} \vspace{0.1in}


\textbf{\href{http://blanketsea.com/2019/09/18/bounded-rationality-by-arnav-sood/}{Bounded Rationality}}. \hfill Blanket Sea
\begin{itemize}
  \setlength{\leftskip}{1cm} \item  Causes and effects of cognitive constraints. Pushcart Prize nominee.
\end{itemize} \vspace{0.1in}

{\vskip 1em}
\bigskip


\setlength{\leftskip}{0cm}
\marginhead{activities}

Volunteer Tech Support, Free Geek Vancouver \vspace{0.1in}

Volunteer Teacher, Splash! (Various Universities)
\begin{itemize}
  \setlength{\leftskip}{1cm}\item ${\color{darkred} \blacktriangleright}$ Taught free one-hour classes to high-school students. Subjects included information economics, statistics, abstract algebra, philosophy of mind, and Play-Doh. \vspace{0.1in}
\end{itemize} 




% \setlength{\leftskip}{1cm}
% \vspace{-0.15in}

% {\vskip 1em}
% \bigskip

% \setlength{\leftskip}{0cm}
% \marginhead{\vskip1.1em honors \\ awards}

% \noindent William Larimer Mellon Fellowship \vspace{0.1in}

% \noindent National Merit Scholarship Competition (Finalist)



\end{document}
